---
title: "R Notebook"
output: html_notebook
---
Read in Data
```{r}
library(ggplot2)
library(Hmisc)
library(readxl)
library(lme4)
library(lmerTest)
library(dplyr)
library(tidyverse)
library(stats)
library(ggthemes)
library(bbmle) #for AICtab()
library(ape)
library(nlme)
library(geiger)
library("phytools")

library(patchwork)
library(emmeans)
library(multcompView)

fiberAngles <- read_excel("Z:/Erin/AllDataMerged.xlsx")
kineMech <- read_excel("Z:/Erin/StiffnessData.xlsx")

fiberAngles <- mutate(fiberAngles, unique.id = paste0(Species, "_", Individual))

forwardAngle <- filter(fiberAngles, Direction ==0)
backwardAngle <- filter(fiberAngles, Direction ==1)

modelTesting <- read_csv("D:/OneDrive/Documents/Dissertation/04.Chapter 3/SkinStats/fibermodel_verification_data_CD.csv")
```

Interpolate fiber angle data for comparison with kinematics and mechanics
```{r}
# TestDatAng <- filter(forwardAngle, unique.id == "Aflavidus_1")
# TestDatMec <- filter(kineMech, unique.id == "Aflavidus_1")
# 
# f = approxfun(x = TestDatAng$Position, y = TestDatAng$Angle, rule = 1, method = 'constant')
# TestDatMec <- mutate(TestDatMec, ForwardFiberAngle = f(Position))
# 
# ggplot() + 
#   geom_point(data = TestDatMec, aes(x = Position, y = ForwardFiberAngle), color = "red") +
#   geom_point(data = TestDatAng, aes(x = Position, y = Angle), color = "blue") 

fiberAngles_kine <- read_excel("Z:/Erin/AllDataMerged_kine.xlsx")
kineMech <- read_excel("Z:/Erin/StiffnessData_fib.xlsx")

fiberAngles_kine <- mutate(fiberAngles_kine, unique.id = paste0(Species, "_", Individual))
kineMech <- mutate(kineMech, GJ = G*J)
kineMech <- mutate(kineMech, unique.id = paste0(Species, "_", Individual))

forwardAngle_kine <- filter(fiberAngles_kine, Direction ==0)
backwardAngle_kine <- filter(fiberAngles_kine, Direction ==1)


##### Forwards Angles ####
kineMech$ForwardFiberAngle <- NA
Individuals = levels(as.factor(forwardAngle_kine$unique.id))
InterpForwardAngles <- data.frame()
for (i in 1:length(Individuals)){
  TestDatAng <- filter(forwardAngle_kine, unique.id == Individuals[i])
  TestDatMec <- filter(kineMech, unique.id == Individuals[i])
  
  f = approxfun(x = TestDatAng$Position, y = TestDatAng$Angle, rule = 2, method = 'linear')
  InterpForwardAngles <- rbind(InterpForwardAngles,
                               as.data.frame(f(TestDatMec$Position)))
}
names(InterpForwardAngles)[1] <- "ForwardFiberAngle"
kineMech$ForwardFiberAngle <- InterpForwardAngles$ForwardFiberAngle
######

##### Backwards Angles ####
kineMech$BackwardFiberAngle <- NA
Individuals = levels(as.factor(backwardAngle_kine$unique.id))
InterpBackwardAngles <- data.frame()
for (i in 1:length(Individuals)){
  TestDatAng <- filter(backwardAngle_kine, unique.id == Individuals[i])
  TestDatMec <- filter(kineMech, unique.id == Individuals[i])
  
  f = approxfun(x = TestDatAng$Position, y = TestDatAng$Angle, rule = 2, method = 'linear')
  InterpBackwardAngles <- rbind(InterpBackwardAngles,
                               as.data.frame(f(TestDatMec$Position)))
}
names(InterpBackwardAngles)[1] <- "BackwardFiberAngle"
kineMech$BackwardFiberAngle <- InterpBackwardAngles$BackwardFiberAngle

```

Mechanics and Kinematics Statistics (everything included)
```{r}
#### Forward Fiber Angle
# FFwobble.anova <- aov(Wobble ~ Position + Species + ForwardFiberAngle + Position:ForwardFiberAngle + Position:Species:ForwardFiberAngle, data = kineMech)
# anova(FFwobble.anova)
# 
# FFG.anova <- aov(G ~ Position + Species + ForwardFiberAngle + Position:ForwardFiberAngle + Position:Species:ForwardFiberAngle, data = kineMech)
# anova(FFG.anova)
# 
# FFGJ.anova <- aov(GJ ~ Position + Species + ForwardFiberAngle + Position:ForwardFiberAngle + Position:Species:ForwardFiberAngle, data = kineMech)
# anova(FFGJ.anova)

#### Backward Fiber Angle
# BFwobble.anova <- aov(Wobble ~ Position + Species + BackwardFiberAngle + Position:BackwardFiberAngle + Position:Species:BackwardFiberAngle,  data = kineMech)
# anova(BFwobble.anova)
# 
# BFG.anova <- aov(G ~ Position + Species + BackwardFiberAngle + Position:BackwardFiberAngle + Position:Species:BackwardFiberAngle, data = kineMech)
# anova(BFG.anova)
# 
# BFGJ.anova <- aov(GJ ~ Position + Species + BackwardFiberAngle + Position:BackwardFiberAngle + Position:Species:BackwardFiberAngle, data = kineMech)
# anova(BFGJ.anova)

#### All Fiber Angles
wobble.anova <- aov(Wobble ~ Position + Species + BackwardFiberAngle + ForwardFiberAngle + Position:BackwardFiberAngle + Position:ForwardFiberAngle + Position:Species:BackwardFiberAngle + Position:Species:ForwardFiberAngle,  data = kineMech)
anova(wobble.anova)

G.anova <- aov(G ~ Position + Species + BackwardFiberAngle + ForwardFiberAngle + Position:BackwardFiberAngle + Position:ForwardFiberAngle + Position:Species:BackwardFiberAngle + Position:Species:ForwardFiberAngle, data = kineMech)
anova(G.anova)

GJ.anova <- aov(GJ ~ Position + Species + BackwardFiberAngle + ForwardFiberAngle + Position:BackwardFiberAngle + Position:ForwardFiberAngle + Position:Species:BackwardFiberAngle + Position:Species:ForwardFiberAngle, data = kineMech)
anova(GJ.anova)
```

Replace Species with Habitat
```{r}
#### Forward Fiber Angle
FFwobble.anova3 <- aov(Wobble ~ Position + Habitat + ForwardFiberAngle + Position:ForwardFiberAngle + Position:Habitat:ForwardFiberAngle, data = kineMech)
anova(FFwobble.anova3)

FFG.anova3 <- aov(G ~ Position + Habitat + ForwardFiberAngle + Position:ForwardFiberAngle + Position:Habitat:ForwardFiberAngle, data = kineMech)
anova(FFG.anova3)

FFGJ.anova3 <- aov(GJ ~ Position + Habitat + ForwardFiberAngle + Position:ForwardFiberAngle + Position:Habitat:ForwardFiberAngle, data = kineMech)
anova(FFGJ.anova3)

#### Backward Fiber Angle
BFwobble.anova3 <- aov(Wobble ~ Position + Habitat + BackwardFiberAngle + Position:BackwardFiberAngle + Position:Habitat:BackwardFiberAngle,  data = kineMech)
anova(BFwobble.anova3)

BFG.anova3 <- aov(G ~ Position + Habitat + BackwardFiberAngle + Position:BackwardFiberAngle + Position:Habitat:BackwardFiberAngle, data = kineMech)
anova(BFG.anova3)

BFGJ.anova3 <- aov(GJ ~ Position + Habitat + BackwardFiberAngle + Position:BackwardFiberAngle + Position:Habitat:BackwardFiberAngle, data = kineMech)
anova(BFGJ.anova3)

#### All Fiber Angles
wobble.anova <- aov(Wobble ~ Position + Habitat + BackwardFiberAngle + ForwardFiberAngle + Position:BackwardFiberAngle + Position:ForwardFiberAngle + Position:Habitat:BackwardFiberAngle + Position:Habitat:ForwardFiberAngle,  data = kineMech)
anova(wobble.anova)

G.anova <- aov(G ~ Position + Habitat + BackwardFiberAngle + ForwardFiberAngle + Position:BackwardFiberAngle + Position:ForwardFiberAngle + Position:Habitat:BackwardFiberAngle + Position:Habitat:ForwardFiberAngle, data = kineMech)
anova(G.anova)

GJ.anova <- aov(GJ ~ Position + Habitat + BackwardFiberAngle + ForwardFiberAngle + Position:BackwardFiberAngle + Position:ForwardFiberAngle + Position:Habitat:BackwardFiberAngle + Position:Habitat:ForwardFiberAngle, data = kineMech)
anova(GJ.anova)
```

Morpholohy Statistics
```{r}
# res.aov2 <- aov(Angle ~ Position + Species + Position:Species, data = forwardAngle)
# anova(res.aov2)
# 
# res.aov3 <- aov(Angle ~ Position + Species + Position:Species, data = backwardAngle)
# anova(res.aov3)
# 
# res.aov4 <- aov(Angle ~ Position + Species + as.factor(Direction) + Position:Species + Position:as.factor(Direction) +
#                   as.factor(Direction):Species + as.factor(Direction):Species:Position, data = fiberAngles)
# anova(res.aov4)

# aov(Y ~ A/B, data=d)
# aov(Y ~ A + B %in% A, data=d)
# aov(Y ~ A + A:B, data=d)

res.aov5 <- aov(Angle ~ Position + Species %in% Habitat + as.factor(Direction) + Position:Species %in% Habitat + Position:as.factor(Direction) +
                  as.factor(Direction):Species %in% Habitat + 
                  as.factor(Direction):Species %in% Habitat:Position, 
                  data = fiberAngles)
anova(res.aov5)
```

Bending Tests Statistics
```{r}
bendingAnovaEI <- lmer(EI ~ Angle * Frequency + (1 | Number), data = modelTesting)
anova(bendingAnovaEI)
summary(bendingAnovaEI)

bendingAnovaE <- lmer(E ~ Angle + Frequency + Amplitude + (1 | Number), data = modelTesting)
anova(bendingAnovaEI)
```

%%%%%% START Old Stats Code %%%%%%%
Phylo-Stats
```{r}
# tree <- read.tree(file="actinopt_12k_treePL.tre")
# my.data <- fiberAngles[fiberAngles$Species %in% tree$tip.label,] # removes species from dataset that are not in tree
# pruned.tree <-drop.tip(tree,tree$tip.label[-match(my.data$Species, tree$tip.label)]) # prunes tree to only include species in your data; FYI, there is a new "keep.tip" function in the latest version of ape that is the inverse of this.
# tree <- pruned.tree
# 
# my.data <- column_to_rownames(my.data, var="Species")
# 
# length(tree$tip.label)
# nrow(my.data)
# 
# bm<-corBrownian(1, tree)
# modelo1<-gls(Angle ~ Position, data=my.data, correlation=bm)
# summary(modelo1)
```

Mechanics and Kinematics Statistics (Species and Angle only)
```{r}
#### Forward Fiber Angle
# FFwobble.anova1 <- aov(Wobble ~ Species + ForwardFiberAngle + Species:ForwardFiberAngle, data = kineMech)
# anova(FFwobble.anova1)
# 
# FFG.anova1 <- aov(G ~ Species + ForwardFiberAngle + Species:ForwardFiberAngle, data = kineMech)
# anova(FFG.anova1)
# 
# FFGJ.anova1 <- aov(GJ ~ Species + ForwardFiberAngle + Species:ForwardFiberAngle, data = kineMech)
# anova(FFGJ.anova1)
# 
# #### Backward Fiber Angle
# BFwobble.anova1 <- aov(Wobble ~ Species + BackwardFiberAngle + Species:BackwardFiberAngle,  data = kineMech)
# anova(BFwobble.anova1)
# 
# BFG.anova1 <- aov(G ~ Species + BackwardFiberAngle + Species:BackwardFiberAngle, data = kineMech)
# anova(BFG.anova1)
# 
# BFGJ.anova1 <- aov(GJ ~ Species + BackwardFiberAngle + Species:BackwardFiberAngle, data = kineMech)
# anova(BFGJ.anova1)
```

Mechanics and Kinematics Statistics (Angle alone removed)
```{r}
# #### Forward Fiber Angle
# FFwobble.anova2 <- aov(Wobble ~ Position + Species + Position:ForwardFiberAngle, data = kineMech)
# anova(FFwobble.anova2)
# 
# FFG.anova2 <- aov(G ~ Position + Species + Position:ForwardFiberAngle, data = kineMech)
# anova(FFG.anova2)
# 
# FFGJ.anova2 <- aov(GJ ~ Position + Species + Position:ForwardFiberAngle, data = kineMech)
# anova(FFGJ.anova2)
# 
# #### Backward Fiber Angle
# BFwobble.anova2 <- aov(Wobble ~ Position + Species  + Position:BackwardFiberAngle,  data = kineMech)
# anova(BFwobble.anova2)
# 
# BFG.anova2 <- aov(G ~ Position + Species + Position:BackwardFiberAngle, data = kineMech)
# anova(BFG.anova2)
# 
# BFGJ.anova2 <- aov(GJ ~ Position + Species + Position:BackwardFiberAngle, data = kineMech)
# anova(BFGJ.anova2)
```

Which model fits best? (AIC table)
```{r}

# AICtab(FFwobble.anova, FFwobble.anova1, FFwobble.anova2, FFwobble.anova3)
# AICtab(FFG.anova, FFG.anova1, FFG.anova2, FFG.anova3)
# AICtab(FFGJ.anova, FFGJ.anova1, FFGJ.anova2, FFGJ.anova3)
# 
# AICtab(BFwobble.anova, BFwobble.anova1, BFwobble.anova2, BFwobble.anova3)
# AICtab(BFG.anova, BFG.anova1, BFG.anova2, BFG.anova3)
# AICtab(BFGJ.anova, BFGJ.anova1, BFGJ.anova2, BFGJ.anova3)

```

Create a data frame with coeficieints of fit lines to attempt cleaner plots
```{r}
# PLSdataFrame <- kineMech %>%
#     group_by(unique.id) %>% #for each individual...
#     summarise(X.FFA.I = lm(ForwardFiberAngle ~ poly(Position, 1)) %>% coef() %>% .[1],  #fit a polynomial, get coeficient
#               X.FFA.p1 = lm(ForwardFiberAngle ~ poly(Position, 1)) %>% coef() %>% .[2], #...slot 2
#               X.FFA.mean = mean(ForwardFiberAngle,na.rm = TRUE), #...slot 3
#               X.BFA.I = lm(BackwardFiberAngle ~ poly(Position, 1)) %>% coef() %>% .[1],
#               X.BFA.p1 = lm(BackwardFiberAngle ~ poly(Position, 1)) %>% coef() %>% .[2],
#               X.BFA.mean = mean(BackwardFiberAngle,na.rm = TRUE),
#               X.Wob.I = lm(Wobble ~ poly(Position, 1)) %>% coef() %>% .[1],
#               X.Wob.p1 = lm(Wobble ~ poly(Position, 1)) %>% coef() %>% .[2],
#               X.Wob.mean = mean(Wobble,na.rm = TRUE),
#               X.GJ.I = lm(GJ ~ poly(Position, 1)) %>% coef() %>% .[1],
#               X.GJ.p1 = lm(GJ ~ poly(Position, 1)) %>% coef() %>% .[2],
#               X.GJ.mean = mean(GJ,na.rm = TRUE),
#               X.G.I = lm(G ~ poly(Position, 1)) %>% coef() %>% .[1],
#               X.G.p1 = lm(G ~ poly(Position, 1)) %>% coef() %>% .[2],
#               X.G.mean = mean(G,na.rm = TRUE)) %>%
#     separate(unique.id, by = "_", into = c("Species", "Individual"))
#   
#   # Get the habitat data back
#   hab_data <- kineMech %>%
#     group_by(Species) %>%
#     summarise(Habitat = first(Habitat))
#   
#   PLSdataFrame <- right_join(PLSdataFrame, hab_data)
```
%%%%%% END Old Stats Code %%%%%%%%%

Kinematics and Mechanics Plots
```{r}
kineMech$WobbleBin <- cut(kineMech$Wobble, c(0, 0.3, 0.6, 1))
kineMech$bin2 <- cut(kineMech$BackwardFiberAngle, c(40, 48, 58, 68, 70))
kineMech$bin3 <- cut(kineMech$ForwardFiberAngle, c(40, 48, 58, 68, 70))
kineMech$PositionBin <-cut(kineMech$Position, c(0, 0.333, 0.666, 1))


ggplot(data = kineMech)+
  geom_point(aes(x=Position, y=ForwardFiberAngle, color=Habitat))+
  #geom_point(aes(x=Position, y=Wobble, color=Habitat))+
  geom_smooth(aes(x=Position, y=ForwardFiberAngle, color=Habitat), method="lm", se=FALSE)+
  geom_smooth(aes(x=Position, y=(Wobble+ 3)*15, color=Habitat),linetype = 2, method="lm", se=FALSE)+
  scale_y_continuous(sec.axis = sec_axis((~./15 - 3), name = "Wobble"))+
  scale_color_economist()+
  theme_minimal()
  ggsave(file="PosVWobandFFA.eps", width = 12, height = 8, units = "cm")

ggplot(data = kineMech)+
  geom_point(aes(x=Position, y=BackwardFiberAngle, color=Habitat))+
  #geom_point(aes(x=Position, y=Wobble, color=Habitat))+
  geom_smooth(aes(x=Position, y=BackwardFiberAngle, color=Habitat), method="lm", se=FALSE)+
  geom_smooth(aes(x=Position, y=(Wobble+ 3)*15, color=Habitat),linetype = 2, method="lm", se=FALSE)+
  scale_y_continuous(sec.axis = sec_axis((~./15 - 3), name = "Wobble"))+
  scale_color_economist()+
  theme_minimal()
  ggsave(file="PosVWobandBFA.eps", width = 12, height = 8, units = "cm")
  
  
  
ggplot(data = kineMech)+
  geom_point(aes(x=Position, y=ForwardFiberAngle, color=Species))+
  geom_smooth(aes(x=Position, y=ForwardFiberAngle, color=Species), method="lm", se=FALSE)+
  scale_color_economist()+
  theme_classic()+
  theme(axis.title.x = element_text(size=12),
      axis.title.y = element_text(size=12),
      axis.text.y = element_text(size=10, color = 'black'),
      axis.text.x = element_text(size=10, color = 'black'),
      axis.line = element_line(size = 1, linetype = "solid"),
      axis.ticks = element_line(size = 1, color = 'black'),
      legend.text=element_text(size=10),
      legend.title = element_text(size=12))+
  ggsave(file="PosVFFAS.eps", width = 12, height = 8, units = "cm")

ggplot(data = kineMech)+
  geom_point(aes(x=Position, y=BackwardFiberAngle, color=Species))+
  geom_smooth(aes(x=Position, y=BackwardFiberAngle, color=Species), method="lm", se=FALSE)+
  scale_color_economist()+
  theme_classic()+
    theme(axis.title.x = element_text(size=12),
      axis.title.y = element_text(size=12),
      axis.text.y = element_text(size=10, color = 'black'),
      axis.text.x = element_text(size=10, color = 'black'),
      axis.line = element_line(size = 1, linetype = "solid"),
      axis.ticks = element_line(size = 1, color = 'black'),
      legend.text=element_text(size=10),
      legend.title = element_text(size=12))+
  ggsave(file="PosVBFAS.eps", width = 12, height = 8, units = "cm")

ggplot(data = kineMech)+
  geom_point(aes(x=Position, y=Wobble, color=Species))+
  geom_smooth(aes(x=Position, y=Wobble, color=Species), method="lm", se=FALSE)+
  scale_color_economist()+
  theme_classic()+
    theme(axis.title.x = element_text(size=12),
      axis.title.y = element_text(size=12),
      axis.text.y = element_text(size=10, color = 'black'),
      axis.text.x = element_text(size=10, color = 'black'),
      axis.line = element_line(size = 1, linetype = "solid"),
      axis.ticks = element_line(size = 1, color = 'black'),
      legend.text=element_text(size=10),
      legend.title = element_text(size=12))+
  ggsave(file="PosVWobS.eps", width = 12, height = 8, units = "cm")

kineMech <- mutate(kineMech, RelFiberAngle = (BackwardFiberAngle+ForwardFiberAngle)/2)

ggplot(data = kineMech)+
  geom_point(aes(x=Position, y=RelFiberAngle, color=Species))+
  geom_smooth(aes(x=Position, y=RelFiberAngle, color=Species), method="lm", se=FALSE)+
  scale_color_economist()+
  theme_classic()+
    theme(axis.title.x = element_text(size=12),
      axis.title.y = element_text(size=12),
      axis.text.y = element_text(size=10, color = 'black'),
      axis.text.x = element_text(size=10, color = 'black'),
      axis.line = element_line(size = 1, linetype = "solid"),
      axis.ticks = element_line(size = 1, color = 'black'),
      legend.text=element_text(size=10),
      legend.title = element_text(size=12))
  ggsave(file="PosVBFAS.eps", width = 12, height = 8, units = "cm")
```

Morphology Scatterplots (All angles)
```{r}
ggplot(forwardAngle, aes(x = Position, y = Angle, color = Species, size=Direction)) +
  geom_point(size = 2) +
  geom_smooth(method = "gam", formula = y ~ poly(x, 2), se = FALSE, size = 2) +
  theme_tufte()+xlab("Position")+ylab("Fiber Angle (degrees)")+
  theme(axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.text.y = element_text(size=20, color = 'black'),
        axis.text.x = element_text(size=20, color = 'black'),
        plot.title = element_text(size=24, face="bold.italic",hjust = 0.5),
        axis.line = element_line(size = 2, linetype = "solid"),
        axis.ticks = element_line(size = 2),
        legend.text=element_text(size=20),
        legend.title = element_text(size=20))

ggplot(backwardAngle, aes(x = Position, y = Angle, color = Species, size=Direction)) +
  geom_point(size = 2) +
  geom_smooth(method = "gam", formula = y ~ poly(x, 2), se = FALSE, size = 2) +
  theme_tufte()+xlab("Position")+ylab("Fiber Angle (degrees)")+
  theme(axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.text.y = element_text(size=20, color = 'black'),
        axis.text.x = element_text(size=20, color = 'black'),
        plot.title = element_text(size=24, face="bold.italic",hjust = 0.5),
        axis.line = element_line(size = 2, linetype = "solid"),
        axis.ticks = element_line(size = 2),
        legend.text=element_text(size=20),
        legend.title = element_text(size=20))
```

Morphology Boxplots (All angles)
```{r}
forwardAngle$bin <- cut(forwardAngle$Position, c(0, 0.3, 0.6, 0.90, 1))
backwardAngle$bin <- cut(backwardAngle$Position, c(0, 0.3, 0.6, 0.90, 1))
head(backwardAngle)

ggplot(data=forwardAngle) + 
  geom_boxplot(aes(x=factor(bin), y=Angle, fill=factor(Species))) +
  geom_smooth(aes(x=as.integer(bin),y=Angle,color=Species),method = "lm", formula = y ~ I(x^2),se=FALSE, size=1)+
  theme_minimal() +
  scale_fill_economist() +
  scale_color_economist() +
  ylab("Angle (degrees)")+
  xlab("Position along Body")+ ggtitle("Forward Facing Angles") +
  guides(fill=guide_legend(title="Species"))+
  geom_hline(yintercept = 45) + 
  geom_hline(yintercept = 55) +
  theme(
    axis.text.x = element_text(size=10),
    axis.text.y = element_text(size=10),
    axis.title.y = element_text(size=12),
    axis.title.x = element_text(size=12),
    legend.text = element_text(size=10),
    legend.title = element_text(size=12),
    plot.title = element_text(size = 12))+
  ylim(5,75)+
  ggsave(file="forwardAngles.eps", width = 10, height = 6, units = "cm")

ggplot(data=backwardAngle) + 
  geom_boxplot(aes(x=factor(bin), y=Angle, fill=factor(Species))) +
  geom_smooth(aes(x=as.integer(bin),y=Angle,color=Species),method = "lm", formula = y ~ I(x^2),se=FALSE, size=1)+
  theme_minimal() +
  scale_fill_economist() +
  scale_color_economist() +
  ylab("Angle (degrees)")+
  xlab("Position along Body")+ ggtitle("Backward Facing Angles") +
  guides(fill=guide_legend(title="Species"))+
  geom_hline(yintercept = 45) + 
  geom_hline(yintercept = 55) +
  theme(
    axis.text.x = element_text(size=10),
    axis.text.y = element_text(size=10),
    axis.title.y = element_text(size=12),
    axis.title.x = element_text(size=12),
    legend.text = element_text(size=10),
    legend.title = element_text(size=12),
    plot.title = element_text(size = 12))+
  ylim(5,75)+
  ggsave(file="backwardAngles.eps", width = 10, height = 6, units = "cm")

```

Bending Plots
```{r}
models.50 <- filter(modelTesting, Frequency %in% c(1, 3, 5))
#models.50 <- filter(models.50, Frequency %in% c(1, 3, 5))

ggplot(data=models.50) + 
  geom_boxplot(aes(x=factor(Angle), y=EI, fill=factor(Frequency))) +
  theme_base()+
  scale_fill_economist() +
  scale_color_economist() +
  guides(fill=guide_legend(title="Bending Frequency"))+
  ylab("Bending Stiffness (Nm^2)") + xlab("Fiber Angle")+
  theme(
     axis.text.x = element_text(size=10),
     axis.text.y = element_text(size=12),
    axis.title.y = element_text(size=12),
    axis.title.x = element_text(size=12),
     legend.text = element_text(size=10),
    legend.title = element_text(size=10),
      plot.title = element_text(size = 12))+
  ggsave(file = "PhysicalModelsVerification.eps", width = 14, height = 8, units = "cm")

```


